---
title: "Interactive maps"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

>Interactive maps of Australian ticks.

Preparing interactive maps for Australian ticks species. 

Maps are produced using [ozmaps](https://github.com/mdsumner/ozmaps) package.

## Curated tick records

Records have been sourced from museum records, literature and Living Atlas Australia. Occurrence records that lie outside of historic distribution records were inspected and curated.

Occurrence records are not always exhaustive but have been curated to ensure that the full distribution of tick species has been investigated.

```{r libraries, include=FALSE}
pkgs <- c("ozmaps", "sf", "sp", "rgdal", "raster",
          "rmapshaper", "ggpubr", "viridis", "plotly",
          "tidyverse", "readxl")
lapply(pkgs, require, character.only = TRUE)
```


```{r include=FALSE}
##########################################
## Am. triguttatum data
##########################################

obs.data.atrig <-
  read_csv("data/tick_records/atrig/compiled_record_list.csv")
obs.data.atrig$Subspecies <- obs.data.atrig$Tick_subspecies

## clean up data

unique(obs.data.atrig$Tick_species)
obs.data.atrig$Tick_species[obs.data.atrig$Tick_species=="`triguttatum (nymph)`"]<-"triguttatum"
obs.data.atrig$Tick_species[obs.data.atrig$Tick_species=="`triguttatum? (juvenile)`"]<-"triguttatum"
obs.data.atrig$Tick_species[obs.data.atrig$Tick_species=="`triguttatum? (nymph)`"]<-"triguttatum"
obs.data.atrig$Tick_species[obs.data.atrig$Tick_species=="`triguttatum? (nymphs)`"]<-"triguttatum"
obs.data.atrig$Tick_species[obs.data.atrig$Tick_species=="`triguttatum?`"]<-"triguttatum"

##########################################
## Ix. holocyclus data
##########################################
obs.data.ixhol <- read_csv(file = "data/tick_records/ixhol/Ixhol-records-2021-02-23/records-2021-02-23-curated.csv")

##########################################
## Ix. tasmani data
##########################################
# curated records
obs.data.ixtas <- read_excel("data/tick_records/ixtas/curated.xlsx")
```



```{r include=FALSE}
##########################################
## Combined record data
##########################################

raw_records <- read_csv("data/tick_records/comb_tick_records.csv")
clean_records <- raw_records

unique(clean_records$STATE)
clean_records$STATE[clean_records$STATE=="W.A."]<-"WA"
clean_records$STATE[clean_records$STATE=="QLD ?"]<-"QLD"
clean_records$STATE[clean_records$STATE=="NSW/QLD"]<-""
clean_records$STATE[clean_records$STATE=="NSW or SA"]<-""
clean_records$STATE[clean_records$STATE=="N.S.W."]<-"NSW"
clean_records$STATE[clean_records$STATE=="Vic"]<-"VIC"
clean_records$STATE[clean_records$STATE=="N.T."]<-"NT"
clean_records$STATE[clean_records$STATE=="Qld"]<-"QLD"
clean_records$STATE[clean_records$STATE=="S.A."]<-"SA"
clean_records$STATE[clean_records$STATE=="Tas."]<-"TAS"
clean_records$STATE[clean_records$STATE=="Vic."]<-"VIC"

#Update and correct taxonomy of tick genus and species names
clean_records$GENUS[clean_records$GENUS=="Aponomma"]<-"Bothriocroton"
clean_records$SPECIES[clean_records$SPECIES=="sanguinensis"]<-"sanguineus"

clean_records$genusspecies <- paste(clean_records$GENUS, clean_records$SPECIES)
unique(clean_records$genusspecies)

#Filter records
comb_records_filt <- clean_records %>%
  filter(!is.na(LATITUDE)) %>%
  filter(!is.na(SPECIES))%>%
  filter(!SPECIES == "sp.")
```


```{r include=FALSE}
### Merge with previous records
df1 <- comb_records_filt %>% 
  select(LATITUDE, LONGITUDE, genusspecies)

df2 <- obs.data.atrig 
df2$genusspecies <- paste(df2$Tick_genus, df2$Tick_species)
df2 <- df2 %>% 
  select(Lat, Lon, genusspecies)
df2 <- rename(df2, 
              LATITUDE = Lat,
              LONGITUDE = Lon)

df3 <- obs.data.ixhol %>% 
  select(Latitude, Longitude, Species)
df3 <- rename(df3, 
              LATITUDE = Latitude,
              LONGITUDE = Longitude,
              genusspecies = Species)

df4 <- obs.data.ixtas
df4$genusspecies <- paste(df4$Tick_genus, df4$Tick_species)
df4 <- df4 %>% 
  select(Lat, Lon, genusspecies)
df4 <- rename(df4, 
              LATITUDE = Lat,
              LONGITUDE = Lon)

tick.obs.data <- rbind(df1, df2, df3, df4)

# remove overseas species
overseas_ticks <- c("Amblyomma soembawensis", "Dermacentor variabilis", "Rhipicephalus appendiculatus", "Rhipicephalus microplus", "Margaropus winthemi", "Argas vespertilionis", "NA NA")

tick.obs.data <- tick.obs.data %>%
  filter(!is.na(LATITUDE)) %>%
  filter(!genusspecies %in% overseas_ticks)
```

```{r include=FALSE}
#Set order for the legend by tick genera.

tick.obs.data$genusspecies <- as.factor(tick.obs.data$genusspecies)

tick.obs.data$genusspecies <-
  factor(
    tick.obs.data$genusspecies,
    levels = c(
      "Amblyomma albolimbatum",
      "Amblyomma australiense",
      "Amblyomma breviscutatum",
      "Amblyomma calabyi",
      "Amblyomma echidnae",
      "Amblyomma fimbriatum",
      "Amblyomma glauerti",
      "Amblyomma limbatum",
      "Amblyomma loculosum",
      "Amblyomma macropi",
      "Amblyomma moreliae",
      "Amblyomma moyi",
      "Amblyomma papuanum",
      "Amblyomma postoculatum",
      "Amblyomma triguttatum",
      "Amblyomma trimaculatum",
      "Amblyomma viikirri",
      "Bothriocroton auruginans",
      "Bothriocroton concolor",
      "Bothriocroton glebopalma",
      "Bothriocroton hydrosauri",
      "Bothriocroton tachyglossi",
      "Bothriocroton undatum",
      "Haemaphysalis bancrofti",
      "Haemaphysalis bremneri",
      "Haemaphysalis doenitzi",
      "Haemaphysalis humerosa",
      "Haemaphysalis lagostrophi",
      "Haemaphysalis longicornis",
      "Haemaphysalis novaeguineae",
      "Haemaphysalis petrogalis",
      "Haemaphysalis ratti",
      "Ixodes antechini",
      "Ixodes auritulus",
      "Ixodes australiensis",
      "Ixodes barkeri",
      "Ixodes confusus",
      "Ixodes cordifer",
      "Ixodes cornuatus",
      "Ixodes eudyptidis",
      "Ixodes fecialis",
      "Ixodes heathi",
      "Ixodes hirsti",
      "Ixodes holocyclus",
      "Ixodes hydromyidis",
      "Ixodes kerguelenensis",
      "Ixodes kohlsi",
      "Ixodes kopsteini",
      "Ixodes laridis",
      "Ixodes myrmecobii",
      "Ixodes ornithorhynchi",
      "Ixodes simplex",
      "Ixodes tasmani",
      "Ixodes trichosuri",
      "Ixodes uriae",
      "Ixodes vestitus",
      "Ixodes victoriensis",
      "Ixodes woyliei",
      "Rhipicephalus australis",
      "Rhipicephalus sanguineus",
      "Argas falco",
      "Argas lagenoplastis",
      "Argas lowryae",
      "Argas nullarborensis",
      "Argas persicus",
      "Argas robertsi",
      "Carios australiensis",
      "Carios capensis",
      "Carios daviesi",
      "Carios dewae",
      "Carios macrodermae",
      "Ornithodoros gurneyi",
      "Ornithodoros macmillani",
      "Otobius megnini"
    )
  )
```


```{r include=FALSE}
#Configure base mapping of Australia

oz_states <- ozmaps::ozmap_states

oz_states <- ozmaps::ozmap_states %>% filter(NAME != "Other Territories")
oz_votes <- rmapshaper::ms_simplify(ozmaps::abs_ced)
```

```{r include=FALSE}
curp <- ggplot() +
  geom_sf(data = oz_votes) +
   geom_sf(data = oz_states, colour = "black", fill = "NA") +
  geom_point(
    data = tick.obs.data,
    mapping = aes(
      x = LONGITUDE,
      y = LATITUDE,
      color = genusspecies
    )) +
  labs(
    x = "Longitude", 
    y = "Latitude", 
    colour = "Tick species",
    title = "Ticks of Australia"
  )

curp1 <- curp + xlim (112,154) + ylim (-45,-8) + theme_classic() + scale_color_viridis(discrete=TRUE)
```
```{r echo=FALSE}
ggplotly(curp1)
```


**Occurrence data of Australian ticks from curated records**

```{r, echo=FALSE}
library(rmarkdown)
tick.obs.data.save <- tick.obs.data %>%
  filter(LATITUDE > -45) %>%
  filter(LATITUDE < -8) %>%
  filter(LONGITUDE > 112) %>%
  filter(LONGITUDE < 154)

tick.obs.data.save <- tick.obs.data.save %>%
  rename(Latitude = LATITUDE, 
         Longitude = LONGITUDE,
         Species = genusspecies)

paged_table(tick.obs.data.save)
```


---

## All Living Atlas Australia records.

Occurrence records from Living Atlas Australia using taxonomic classification "Ixodida" (Order level).

```{r include=FALSE}
obs.data.ala <-
  read_csv("data/tick_records/IXODIDA-records-2022-02-27/records-2022-02-27.csv")

# Filter out data without species and no coordinates
obs.data.ala <- obs.data.ala %>%
  filter(!is.na(species)) %>%
  filter(!is.na(decimalLatitude))

obs.data.ala$species[obs.data.ala$species=="Argas dewae"]<-"Carios dewae"
obs.data.ala$species[obs.data.ala$species=="Argas macrodermae"]<-"Carios macrodermae"

#Set order for the legend by tick genera.

obs.data.ala$species <- as.factor(obs.data.ala$species)

obs.data.ala$species <- factor(
  obs.data.ala$species,
  levels = c(
    "Amblyomma albolimbatum",
    "Amblyomma australiense",
    "Amblyomma calabyi",
    "Amblyomma echidnae",
    "Amblyomma fimbriatum",
    "Amblyomma flavomaculatum",
    "Amblyomma glauerti",
    "Amblyomma limbatum",
    "Amblyomma loculosum",
    "Amblyomma macropi",
    "Amblyomma moreliae",
    "Amblyomma moyi",
    "Amblyomma postoculatum",
    "Amblyomma triguttatum",
    "Amblyomma trimaculatum",
    "Amblyomma viikirri",
    "Bothriocroton auruginans",
    "Bothriocroton concolor",
    "Bothriocroton glebopalma",
    "Bothriocroton hydrosauri",
    "Bothriocroton tachyglossi",
    "Bothriocroton undatum",
    "Haemaphysalis bancrofti",
    "Haemaphysalis humerosa",
    "Haemaphysalis lagostrophi",
    "Haemaphysalis longicornis",
    "Haemaphysalis petrogalis",
    "Haemaphysalis ratti",
    "Ixodes antechini",
    "Ixodes auritulus",
    "Ixodes australiensis",
    "Ixodes cordifer",
    "Ixodes cornuatus",
    "Ixodes eudyptidis",
    "Ixodes fecialis",
    "Ixodes heathi",
    "Ixodes hirsti",
    "Ixodes holocyclus",
    "Ixodes hydromyidis",
    "Ixodes kerguelenensis",
    "Ixodes kohlsi",
    "Ixodes myrmecobii",
    "Ixodes ornithorhynchi",
    "Ixodes tasmani",
    "Ixodes trichosuri",
    "Ixodes uriae",
    "Ixodes victoriensis",
    "Ixodes woyliei",
    "Rhipicephalus australis",
    "Rhipicephalus sanguineus",
    "Argas lagenoplastis",
    "Argas persicus",
    "Argas robertsi",
    "Carios dewae",
    "Carios macrodermae",
    "Ornithodoros gurneyi",
    "Ornithodoros macmillani"
  )
)
```

```{r include=FALSE}
pala <- ggplot() +
  geom_sf(data = oz_votes) +
   geom_sf(data = oz_states, colour = "black", fill = "NA") +
  geom_point(
    data = obs.data.ala,
    mapping = aes(
      x = decimalLongitude,
      y = decimalLatitude,
      color = species
    )) +
  labs(
    x = "Longitude", 
    y = "Latitude", 
    colour = "Tick species",
    title = "Ticks of Australia - Living Atlas Australia Records"
  )

pala1 <- pala + xlim (112,154) + ylim (-45,-8) + theme_classic() + scale_color_viridis(discrete=TRUE)
```
```{r echo=FALSE}
ggplotly(pala1)
```


**Occurrence data of Australian ticks from Living Atlas Australia records**

```{r, echo=FALSE}
library(rmarkdown)
obs.data.ala.save <- obs.data.ala %>%
  filter(decimalLatitude > -45) %>%
  filter(decimalLatitude < -8) %>%
  filter(decimalLongitude > 112) %>%
  filter(decimalLongitude < 154)

obs.data.ala.save <- obs.data.ala.save %>%
  select(decimalLatitude, decimalLongitude, species)

obs.data.ala.save <- obs.data.ala.save %>%
  rename(Latitude = decimalLatitude, 
         Longitude = decimalLongitude,
         Species = species)

paged_table(obs.data.ala.save)
```



