---
title: "Mapping"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
    code_folding: hide
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning=FALSE)
```


# Individual species map

Preparing individual species map for three wide spread tick species in Australia. Maps are produced using [ozmaps](https://github.com/mdsumner/ozmaps) package.

Records have been sourced from museum records, literature and Living Atlas Australia. Occurrence records that lie outside of historic distribution records were inspected and curated.

Occurrence records are not always exhaustive but have been curated to ensure that the full distribution of tick species has been investigated.

**Load libraries**
```{r libraries, message=FALSE, warning=FALSE, results='hide'}
pkgs <- c("ozmaps", "sf", "sp", "rgdal", "raster",
          "rmapshaper", "ggpubr", "viridis", "plotly",
          "tidyverse", "readxl")
lapply(pkgs, require, character.only = TRUE)
```

Configure base mapping of Australia

```{r}
oz_states <- ozmaps::ozmap_states
oz_states <-
  ozmaps::ozmap_states %>% filter(NAME != "Other Territories")
oz_votes <- rmapshaper::ms_simplify(ozmaps::abs_ced)
p <- ggplot() +
  geom_sf(data = oz_states,
          mapping = aes(fill = NAME),
          show.legend = FALSE) +
  geom_sf(data = oz_votes, fill = NA) +
  coord_sf()
```

## *Amblyomma triguttatum* records

Load data
```{r}
obs.data.atrig <-
  read_csv("data/tick_records/atrig/compiled_record_list.csv")
obs.data.atrig$Subspecies <- obs.data.atrig$Tick_subspecies

## clean up data

unique(obs.data.atrig$Tick_species)
obs.data.atrig$Tick_species[obs.data.atrig$Tick_species == "`triguttatum (nymph)`"] <-
  "triguttatum"
obs.data.atrig$Tick_species[obs.data.atrig$Tick_species == "`triguttatum? (juvenile)`"] <-
  "triguttatum"
obs.data.atrig$Tick_species[obs.data.atrig$Tick_species == "`triguttatum? (nymph)`"] <-
  "triguttatum"
obs.data.atrig$Tick_species[obs.data.atrig$Tick_species == "`triguttatum? (nymphs)`"] <-
  "triguttatum"
obs.data.atrig$Tick_species[obs.data.atrig$Tick_species == "`triguttatum?`"] <-
  "triguttatum"
```


Create a map showing different subspecies of *Am. triguttatum*

Make map with state and voting outlines, overlay with all observation data

### Combined *Am. triguttatum* maps

**Use colour/shape to show subspecies**
```{r}
Atrig1 = ggplot() +
  geom_sf(data = oz_votes) +
  geom_sf(data = oz_states) +
  geom_point(
    data = obs.data.atrig,
    mapping = aes(
      x = Lon,
      y = Lat,
      shape = Subspecies,
      color = Subspecies,
      stroke = 1
    )
  )

# Customise scale
Atrig1 = Atrig1 + coord_sf() + theme_bw() + theme(axis.title.x = element_blank(),
                                                  axis.title.y = element_blank()) +
  scale_color_manual(values = c("#252525", "#1b9e77", "#e7298a", "#66a61e", "#7570b3")) +
  scale_shape_manual(values = c(16, 17, 15, 3, 7)) + xlim (111, 155)
Atrig1

# Map without legend
Atrig2 <- Atrig1 + theme(legend.position = "none") + xlim (111, 155)
```

```{r, eval=FALSE}
# Save
ggsave(
  "map-atrig-subspecies1.pdf",
  plot = Atrig1,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)
ggsave(
  "map-atrig-subspecies2.pdf",
  plot = Atrig2,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)
```

**Make simple map grouping all subspecies**
```{r}
Atrig3 = ggplot() +
  geom_sf(data = oz_votes) +
  geom_sf(data = oz_states,
          colour = "black",
          fill = "NA") +
  geom_point(data = obs.data.atrig,
             mapping = aes(
               x = Lon,
               y = Lat,
               color = "#7570b3",
               stroke = 1
             )) 
# Customise scale
Atrig3 = Atrig3 + coord_sf() + theme_bw() + theme(
  legend.position = "none",
  axis.title.x = element_blank(),
  axis.title.y = element_blank()
)  + scale_color_manual(values = c("#7570b3")) + xlim (111,155)
Atrig3

# Remove scale
Atrig4 = Atrig3 + coord_sf() + theme_void() + theme(legend.position = "none")  + scale_color_manual(values = c("#7570b3")) +
  xlim (111,155)
```
Save map
```{r, eval=FALSE}
ggsave(
  "map-atrig1.pdf",
  plot = Atrig3,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)
ggsave(
  "map-atrig2.pdf",
  plot = Atrig4,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)
```

### Facet by *Am. triguttatum* subspecies map

Uee data with subspecies info and subset map

```{r}
# Filter out data where subspecies is not specified
obs.data.ssp = filter(obs.data.atrig, Subspecies != "Not specified")

# make master plot
Atrig5 = ggplot() +
  geom_sf(data = oz_votes) +
  geom_sf(data = oz_states,
          colour = "black",
          fill = "NA") +
  geom_point(
    data = obs.data.ssp,
    mapping = aes(
      x = Lon,
      y = Lat,
      shape = Subspecies,
      color = Subspecies,
      stroke = 1
    )
  ) +
  coord_sf() + theme_bw() +
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  ) +
  scale_color_manual(values = c("#1b9e77", "#e7298a", "#66a61e", "#7570b3")) +
  scale_shape_manual(values = c(17, 15, 3, 7)) + xlim (111, 155)
# Facet
Atrig5 = Atrig5 + facet_wrap( ~ Subspecies)
Atrig5
```

```{r, eval=FALSE}
# Save
ggsave(
  "map-atrig-facet.pdf",
  plot = Atrig5,
  path = "output/plots",
  width = 30,
  height = 20,
  units = "cm"
)
```

## Map of *Ixodes holocyclus* records

Load data
```{r}
# raw ala records
ixhol.ala <-
  read_csv(file = "data/tick_records/ixhol/Ixhol-records-2021-02-23/records-2021-02-23.csv")
# curated ala records - removed likely incorrect (or as a result of travel?) records from WA, SA and TAS.
obs.data.ixhol <-
  read_csv(file = "data/tick_records/ixhol/Ixhol-records-2021-02-23/records-2021-02-23-curated.csv")
```

Make map with state and voting outlines, overlay with all observation data
```{r}
Ixhol = ggplot() +
  geom_sf(data = oz_votes) +
  geom_sf(data = oz_states,
          colour = "black",
          fill = "NA") +
  geom_point(
    data = obs.data.ixhol,
    mapping = aes(
      x = Longitude,
      y = Latitude,
      color = "#d95f02",
      stroke = 1
    )
  )
# Customise scale
Ixhol1 = Ixhol + coord_sf() + theme_bw() + theme(
  legend.position = "none",
  axis.title.x = element_blank(),
  axis.title.y = element_blank()
)  + scale_color_manual(values = c("#d95f02")) + xlim (111, 155)
Ixhol1
# Remove scale
Ixhol2 = Ixhol + coord_sf() + theme_void() + theme(legend.position = "none")  + scale_color_manual(values =
                                                                                                     c("#d95f02")) + xlim (111, 155)
```
Save maps
```{r, eval=FALSE}
ggsave(
  "map-ixhol1.pdf",
  plot = Ixhol1,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)
ggsave(
  "map-ixhol2.pdf",
  plot = Ixhol2,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)
```

## Map of *Ixodes tasmani* records

Load data
```{r}
# curated records
obs.data.ixtas <- read_excel("data/tick_records/ixtas/curated.xlsx")
```

Make map with state and voting outlines, overlay with all observation data
```{r}
Ixtas = ggplot() +
  geom_sf(data = oz_votes) +
  geom_sf(data = oz_states,
          colour = "black",
          fill = "NA") +
  geom_point(data = obs.data.ixtas,
             mapping = aes(
               x = Lon,
               y = Lat,
               color = "#a6761d",
               stroke = 1
             ))
# Customise scale
Ixtas1 = Ixtas + coord_sf() + theme_bw() + theme(
  legend.position = "none",
  axis.title.x = element_blank(),
  axis.title.y = element_blank()
)  + scale_color_manual(values = c("#a6761d"))  + xlim (111, 155)
Ixtas1
# Remove scale
Ixtas2 = Ixtas1 + coord_sf() + theme_void() + theme(legend.position = "none")  + scale_color_manual(values =
                                                                                                      c("#a6761d")) + xlim (111, 155)
```
Save maps
```{r, eval=FALSE}
ggsave(
  "map-ixtas1.pdf",
  plot = Ixtas1,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)
ggsave(
  "map-ixtas2.pdf",
  plot = Ixtas2,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)
```

# Combined map

Make combine map of *Am. trig*, *Ix. hol* and *Ix. tas*.

## Using *Am. triguttatum* subspecies maps

```{r, eval=FALSE}
figure1 <- ggarrange(
  Atrig2,
  Ixhol1,
  Ixtas1,
  labels = c("A", "B", "C"),
  ncol = 2,
  nrow = 2
)
ggsave(
  "combined-map1.pdf",
  plot = figure1,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)
figure1

figure2 <- ggarrange(Atrig2,
                     Ixhol1,
                     Ixtas1,
                     labels = c("A", "B", "C"),
                     nrow = 3)
ggsave(
  "combined-map2.pdf",
  plot = figure2,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)
figure2

figure3 <- ggarrange(Atrig2,
                     Ixhol1,
                     Ixtas1,
                     labels = c("A", "B", "C"),
                     ncol = 3)
ggsave(
  "combined-map3.pdf",
  plot = figure3,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)
figure3
```

```{r, eval=FALSE}
gp <- ggarrange(
  Atrig2,
  # First row with line plot
  # Second row with box and dot plots
  ggarrange(Ixhol1, Ixtas1, ncol = 2, labels = c("B", "C")),
  nrow = 2,
  labels = "A"       # Label of the line plot
)
gp

ggsave(
  "combined-map4.pdf",
  plot = gp,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)
```

## Using *Am. triguttatum* combine maps

```{r, eval=FALSE}
figure1 <- ggarrange(
  Atrig3,
  Ixhol1,
  Ixtas1,
  labels = c("A", "B", "C"),
  ncol = 2,
  nrow = 2
)
ggsave(
  "combined-map5.pdf",
  plot = figure1,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)
figure1

figure2 <- ggarrange(Atrig3,
                     Ixhol1,
                     Ixtas1,
                     labels = c("A", "B", "C"),
                     nrow = 3)
ggsave(
  "combined-map6.pdf",
  plot = figure2,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)
figure2

figure3 <- ggarrange(Atrig3,
                     Ixhol1,
                     Ixtas1,
                     labels = c("A", "B", "C"),
                     ncol = 3)
ggsave(
  "combined-map7.pdf",
  plot = figure3,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)
figure3
```

```{r, eval=FALSE}
gp <- ggarrange(
  Atrig3,
  # First row with line plot
  # Second row with box and dot plots
  ggarrange(Ixhol1, Ixtas1, ncol = 2, labels = c("B", "C")),
  nrow = 2,
  labels = "A"       # Label of the line plot
)
gp

ggsave(
  "combined-map8.pdf",
  plot = gp,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)
```



-----

# All records of Australian ticks

## Curated data

> First set of plots contains occurance data from curated plots
Load data which contains combined records from ANIC, WAM, Living Atlas Australia and publications.


```{r}
raw_records <- read_csv("data/tick_records/comb_tick_records.csv")
head(raw_records)
```


### Clean up data

Correct states
```{r}
clean_records <- raw_records

unique(clean_records$STATE)
clean_records$STATE[clean_records$STATE == "W.A."] <- "WA"
clean_records$STATE[clean_records$STATE == "QLD ?"] <- "QLD"
clean_records$STATE[clean_records$STATE == "NSW/QLD"] <- ""
clean_records$STATE[clean_records$STATE == "NSW or SA"] <- ""
clean_records$STATE[clean_records$STATE == "N.S.W."] <- "NSW"
clean_records$STATE[clean_records$STATE == "Vic"] <- "VIC"
clean_records$STATE[clean_records$STATE == "N.T."] <- "NT"
clean_records$STATE[clean_records$STATE == "Qld"] <- "QLD"
clean_records$STATE[clean_records$STATE == "S.A."] <- "SA"
clean_records$STATE[clean_records$STATE == "Tas."] <- "TAS"
clean_records$STATE[clean_records$STATE == "Vic."] <- "VIC"
```

Update and correct taxonomy of tick genus and species names
```{r}
clean_records$GENUS[clean_records$GENUS == "Aponomma"] <-
  "Bothriocroton"
clean_records$SPECIES[clean_records$SPECIES == "sanguinensis"] <-
  "sanguineus"

clean_records$genusspecies <-
  paste(clean_records$GENUS, clean_records$SPECIES)
unique(clean_records$genusspecies)
```

Filter records
```{r}
comb_records_filt <- clean_records %>%
  filter(!is.na(LATITUDE)) %>%
  filter(!is.na(SPECIES)) %>%
  filter(!SPECIES == "sp.")
```


### Merge with previous records

Merge full records with curated records for *Am. triguttatum*, *Ix. holocyclus* and *Ix. tasmani*.
```{r}
df1 <-
  comb_records_filt %>% select(LATITUDE, LONGITUDE, genusspecies)

df2 <- obs.data.atrig
df2$genusspecies <- paste(df2$Tick_genus, df2$Tick_species)
df2 <- df2 %>% select(Lat, Lon, genusspecies)
df2 <- rename(df2,
              LATITUDE = Lat,
              LONGITUDE = Lon)

df3 <- obs.data.ixhol %>% select(Latitude, Longitude, Species)
df3 <- rename(df3,
              LATITUDE = Latitude,
              LONGITUDE = Longitude,
              genusspecies = Species)

df4 <- obs.data.ixtas
df4$genusspecies <- paste(df4$Tick_genus, df4$Tick_species)
df4 <- df4 %>% select(Lat, Lon, genusspecies)
df4 <- rename(df4,
              LATITUDE = Lat,
              LONGITUDE = Lon)

tick.obs.data <- rbind(df1, df2, df3, df4)
```

Final filter of records - also filtering single record of *Argas vespertilionis* in WAM database - I think given single record this is most likely an incorrect identification.
```{r}
# # remove overseas species
overseas_ticks <-
  c(
    "Amblyomma soembawensis",
    "Dermacentor variabilis",
    "Rhipicephalus appendiculatus",
    "Rhipicephalus microplus",
    "Margaropus winthemi",
    "Argas vespertilionis",
    "NA NA"
  )

tick.obs.data <- tick.obs.data %>%
  filter(!is.na(LATITUDE)) %>%
  filter(!genusspecies %in% overseas_ticks)
```


### Plot

Make combined plot of all tick species recorded in Australia.
```{r}
oz_states <- ozmaps::ozmap_states

oz_states <-
  ozmaps::ozmap_states %>% filter(NAME != "Other Territories")
oz_votes <- rmapshaper::ms_simplify(ozmaps::abs_ced)
```

Set order for the legend by tick genera.
```{r}
levels(tick.obs.data$genusspecies)
tick.obs.data$genusspecies <- as.factor(tick.obs.data$genusspecies)
levels(tick.obs.data$genusspecies)

tick.obs.data$genusspecies <-
  factor(
    tick.obs.data$genusspecies,
    levels = c(
      "Amblyomma albolimbatum",
      "Amblyomma australiense",
      "Amblyomma breviscutatum",
      "Amblyomma calabyi",
      "Amblyomma echidnae",
      "Amblyomma fimbriatum",
      "Amblyomma glauerti",
      "Amblyomma limbatum",
      "Amblyomma loculosum",
      "Amblyomma macropi",
      "Amblyomma moreliae",
      "Amblyomma moyi",
      "Amblyomma papuanum",
      "Amblyomma postoculatum",
      "Amblyomma triguttatum",
      "Amblyomma trimaculatum",
      "Amblyomma viikirri",
      "Bothriocroton auruginans",
      "Bothriocroton concolor",
      "Bothriocroton glebopalma",
      "Bothriocroton hydrosauri",
      "Bothriocroton tachyglossi",
      "Bothriocroton undatum",
      "Haemaphysalis bancrofti",
      "Haemaphysalis bremneri",
      "Haemaphysalis doenitzi",
      "Haemaphysalis humerosa",
      "Haemaphysalis lagostrophi",
      "Haemaphysalis longicornis",
      "Haemaphysalis novaeguineae",
      "Haemaphysalis petrogalis",
      "Haemaphysalis ratti",
      "Ixodes antechini",
      "Ixodes auritulus",
      "Ixodes australiensis",
      "Ixodes barkeri",
      "Ixodes confusus",
      "Ixodes cordifer",
      "Ixodes cornuatus",
      "Ixodes eudyptidis",
      "Ixodes fecialis",
      "Ixodes heathi",
      "Ixodes hirsti",
      "Ixodes holocyclus",
      "Ixodes hydromyidis",
      "Ixodes kerguelenensis",
      "Ixodes kohlsi",
      "Ixodes kopsteini",
      "Ixodes laridis",
      "Ixodes myrmecobii",
      "Ixodes ornithorhynchi",
      "Ixodes simplex",
      "Ixodes tasmani",
      "Ixodes trichosuri",
      "Ixodes uriae",
      "Ixodes vestitus",
      "Ixodes victoriensis",
      "Ixodes woyliei",
      "Rhipicephalus australis",
      "Rhipicephalus sanguineus",
      "Argas falco",
      "Argas lagenoplastis",
      "Argas lowryae",
      "Argas nullarborensis",
      "Argas persicus",
      "Argas robertsi",
      "Carios australiensis",
      "Carios capensis",
      "Carios daviesi",
      "Carios dewae",
      "Carios macrodermae",
      "Ornithodoros gurneyi",
      "Ornithodoros macmillani",
      "Otobius megnini"
    )
  )
```

```{r}
p <- ggplot() +
  geom_sf(data = oz_votes) +
   geom_sf(data = oz_states, colour = "black", fill = "NA") +
  geom_point(
    data = tick.obs.data,
    mapping = aes(
      x = LONGITUDE,
      y = LATITUDE,
      color = genusspecies
    )) +
  labs(
    x = "Longitude", 
    y = "Latitude", 
    colour = "Tick species",
    title = "Ticks of Australia"
  )

p1 <-
  p + xlim (112, 154) + ylim (-45, -8) + theme_classic() + scale_color_viridis(discrete =
                                                                                 TRUE)

ggplotly(p1)
```

```{r}
p1.plotly <- plotly::ggplotly(p1)

htmlwidgets::saveWidget(p1.plotly, "output/plots/map-all-curated.html")
```


```{r eval=FALSE, include=FALSE}
#### Formatting for saving as pdf version

# theme 1 with scale
allmap1 = p + coord_sf() + theme_bw() + theme(
  legend.position = "none",
  axis.title.x = element_blank(),
  axis.title.y = element_blank()
) + ylim (-45, -8) + xlim (112, 154) + scale_color_viridis(discrete = TRUE)

# theme 2 without scale
allmap2 = allmap1 + coord_sf() + theme_void() + theme(legend.position = "none") + ylim (-45, -8) + xlim (112, 154) + scale_color_viridis(discrete =
                                                                                                                                           TRUE)

# save
ggsave(
  "allmap1.pdf",
  plot = allmap1,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)
ggsave(
  "allmap2.pdf",
  plot = allmap2,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)

#### just save legend
library(grid)
library(gridExtra) 

# format map with legend

maplegend = p + coord_sf() +
  theme_bw() +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  ylim (-45, -8) + xlim (112, 154) +
  scale_color_viridis(discrete = TRUE) +
  theme(legend.text = element_text(size = 7, face = "italic"))

ggsave(
  "maplegend.pdf",
  plot = maplegend,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)

legend <- cowplot::get_legend(maplegend)

grid.newpage()
pdf("output/plots/maplegend.pdf")
grid.draw(legend)
dev.off()
```

#### Data behind the map

Occurrence of data of Australian ticks.

```{r eval=FALSE, include=FALSE}
library(rmarkdown)
tick.obs.data.save <- tick.obs.data %>%
  filter(LATITUDE > -45) %>%
  filter(LATITUDE < -8) %>%
  filter(LONGITUDE > 112) %>%
  filter(LONGITUDE < 154)

paged_table(tick.obs.data.save)
```


---

## All Living Atlas Australia records.

Search of Living Atlas Australia using taxonomic classification "Ixodida" (Order level).

```{r}
obs.data.ala <-
  read_csv("data/tick_records/IXODIDA-records-2022-02-27/records-2022-02-27.csv")

# Filter out data without species and no coordinates
obs.data.ala <- obs.data.ala %>%
  filter(!is.na(species)) %>%
  filter(!is.na(decimalLatitude))
```

```{r}
obs.data.ala$species[obs.data.ala$species=="Argas dewae"]<-"Carios dewae"
obs.data.ala$species[obs.data.ala$species=="Argas macrodermae"]<-"Carios macrodermae"
```

Prepare base map
```{r}
oz_states <- ozmaps::ozmap_states

oz_states <-
  ozmaps::ozmap_states %>% filter(NAME != "Other Territories")
oz_votes <- rmapshaper::ms_simplify(ozmaps::abs_ced)
```

Set order for the legend by tick genera.
```{r}
levels(obs.data.ala$species)
obs.data.ala$species <- as.factor(obs.data.ala$species)
levels(obs.data.ala$species)

obs.data.ala$species <- factor(
  obs.data.ala$species,
  levels = c(
    "Amblyomma albolimbatum",
    "Amblyomma australiense",
    "Amblyomma calabyi",
    "Amblyomma echidnae",
    "Amblyomma fimbriatum",
    "Amblyomma flavomaculatum",
    "Amblyomma glauerti",
    "Amblyomma limbatum",
    "Amblyomma loculosum",
    "Amblyomma macropi",
    "Amblyomma moreliae",
    "Amblyomma moyi",
    "Amblyomma postoculatum",
    "Amblyomma triguttatum",
    "Amblyomma trimaculatum",
    "Amblyomma viikirri",
    "Bothriocroton auruginans",
    "Bothriocroton concolor",
    "Bothriocroton glebopalma",
    "Bothriocroton hydrosauri",
    "Bothriocroton tachyglossi",
    "Bothriocroton undatum",
    "Haemaphysalis bancrofti",
    "Haemaphysalis humerosa",
    "Haemaphysalis lagostrophi",
    "Haemaphysalis longicornis",
    "Haemaphysalis petrogalis",
    "Haemaphysalis ratti",
    "Ixodes antechini",
    "Ixodes auritulus",
    "Ixodes australiensis",
    "Ixodes cordifer",
    "Ixodes cornuatus",
    "Ixodes eudyptidis",
    "Ixodes fecialis",
    "Ixodes heathi",
    "Ixodes hirsti",
    "Ixodes holocyclus",
    "Ixodes hydromyidis",
    "Ixodes kerguelenensis",
    "Ixodes kohlsi",
    "Ixodes myrmecobii",
    "Ixodes ornithorhynchi",
    "Ixodes tasmani",
    "Ixodes trichosuri",
    "Ixodes uriae",
    "Ixodes victoriensis",
    "Ixodes woyliei",
    "Rhipicephalus australis",
    "Rhipicephalus sanguineus",
    "Argas lagenoplastis",
    "Argas persicus",
    "Argas robertsi",
    "Carios dewae",
    "Carios macrodermae",
    "Ornithodoros gurneyi",
    "Ornithodoros macmillani"
  )
)
```

```{r}
p <- ggplot() +
  geom_sf(data = oz_votes) +
   geom_sf(data = oz_states, colour = "black", fill = "NA") +
  geom_point(
    data = obs.data.ala,
    mapping = aes(
      x = decimalLongitude,
      y = decimalLatitude,
      color = species
    )) +
  labs(
    x = "Longitude", 
    y = "Latitude", 
    colour = "Tick species",
    title = "Ticks of Australia - Living Atlas Australia Records"
  )

p1 <- p + xlim (112,154) + ylim (-45,-8) + theme_classic() + scale_color_viridis(discrete=TRUE)

ggplotly(p1)
```

```{r}
p1.plotly <- plotly::ggplotly(p1)

htmlwidgets::saveWidget(p1.plotly, "output/plots/map-all-ala.html")
```


```{r eval=FALSE, include=FALSE}
#### Formatting for saving as pdf version

# theme 1 with scale
allmapala1 = p + coord_sf() + theme_bw() + theme(
  legend.position = "none",
  axis.title.x = element_blank(),
  axis.title.y = element_blank()
) + ylim (-45, -8) + xlim (112, 154) + scale_color_viridis(discrete = TRUE)

# theme 2 without scale
allmapala2 = allmapala1 + coord_sf() + theme_void() + theme(legend.position = "none") + ylim (-45, -8) + xlim (112, 154) + scale_color_viridis(discrete =
                                                                                                                                                 TRUE)

# save
ggsave(
  "allmapala1.pdf",
  plot = allmapala1,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)
ggsave(
  "allmapala2.pdf",
  plot = allmapala2,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)

#### just save legend
library(grid)
library(gridExtra) 

# format map with legend


maplegend = p + coord_sf() +
  theme_bw() +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  ylim (-45, -8) + xlim (112, 154) +
  scale_color_viridis(discrete = TRUE) +
  theme(legend.text = element_text(size = 7, face = "italic"))

ggsave(
  "maplegend-ala.pdf",
  plot = maplegend,
  path = "output/plots",
  width = 30,
  height = 15,
  units = "cm"
)
```


```{r eval=FALSE, include=FALSE}
library(rmarkdown)
obs.data.ala.save <- obs.data.ala %>%
  filter(decimalLatitude > -45) %>%
  filter(decimalLatitude < -8) %>%
  filter(decimalLongitude > 112) %>%
  filter(decimalLongitude < 154)

paged_table(obs.data.ala.save)
```


